MassWateR: Improving quality control, analysis, and sharing of water quality data

### 2023-07-13 paper.Rmd
fix figure dimensions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(MassWateR)
library(flextable)
library(dplyr)
library(here)

@@

```{r importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.', fig.alt='Diagram showing pseudocode for importing a data file with MassWateR', out.width='100%'}
knitr::include_graphics('figs/importflow.png')
```

@@

```{r, results = 'hide', echo = T}
library(MassWateR)

# import results data
respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
resdat <- readMWRresults(respth)

@@

```{r, fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
```

@@

```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
anlzMWRseason(fset = fsetls, param = "DO", thresh = "fresh", 
  group = "month", type = "jitterbox")
```

@@

```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
anlzMWRdate(fset = fsetls, param = 'DO', group = 'locgroup', 
  thresh = 'fresh')
```

@@

```{r fig.height = 3, fig.width = 6, echo = T, out.width = '100%'}
anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box", 
  site = c("ABT-026", "ABT-062", "ABT-077", "ABT-144", "ABT-237", "ABT-301"),
  resultatt = c('DRY', 'WET'), byresultatt = TRUE)
```

@@

```{r fig.height = 6, fig.width = 6, echo = T, out.width = '100%'}
anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(flextable)
library(dplyr)
library(here)

@@

```{r importflow, fig.cap = 'Pseudocode demonstrating the iterative process of importing a required data file for \\CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).', fig.alt='Diagram showing pseudocode for importing and fixing a data file with MassWateR', out.width='100%'}
knitr::include_graphics('figs/importflow.png')
```

@@

```{r, results = 'hide', echo = T}
# import results data
respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
resdat <- readMWRresults(respth)

@@

```{r, fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
anlzMWRoutlier(fset = fsetls, param = "DO", group = "month")
```

@@

```{r fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
anlzMWRseason(fset = fsetls, param = "DO", thresh = "fresh", 
  group = "month", type = "jitterbox")
```

@@

```{r fig.height = 4, fig.width = 8, echo = T, out.width = '95%', fig.align = 'center'}
anlzMWRdate(fset = fsetls, param = 'DO', group = 'locgroup', 
  thresh = 'fresh')
```

@@

```{r fig.height = 4, fig.width = 8, echo = T,  out.width = '95%', fig.align = 'center'}
anlzMWRsite(fset = fsetls, param = "DO", thresh = "fresh", type = "box", 
  site = c("ABT-026", "ABT-062", "ABT-077", "ABT-144", "ABT-237", "ABT-301"),
  resultatt = c('DRY', 'WET'), byresultatt = TRUE)
```

@@

```{r fig.height = 5, fig.width = 5, echo = T, out.width = '95%', fig.align = 'center'}
anlzMWRmap(fset = fsetls, param = "DO", addwater = "medium")
```

### 2023-07-13 paper.tex
fix figure dimensions

\begin{figure}
\includegraphics[width=1\linewidth]{figs/importflow} \caption{Pseudocode demonstrating the iterative process of importing a required data file for \CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned.}\label{fig:importflow}
\end{figure}

@@

# import results data
respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
resdat <- readMWRresults(respth)

@@

\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1}

@@

\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-11-1}

@@

\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-12-1}

@@

\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-13-1}

@@

\includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-14-1}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{figs/importflow} \caption{Pseudocode demonstrating the iterative process of importing a required data file for \CRANpkg{MassWateR}.  All read functions import an Excel file and the imported file is then passed to a check function.  The function exits if an error is encountered, allowing the user to manually fix the identified error and then import again.  After all checks are passed, a formatting function is applied to correct minor issues (e.g., standardize date format as YYYY-MM-DD) and the final data object is returned (e.g., `resdat`).}\label{fig:importflow}
\end{figure}

@@

\begin{verbatim}
# import results data
respth <- system.file("extdata/ExampleResults.xlsx", package = "MassWateR")
resdat <- readMWRresults(respth)

@@

\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1} \end{center}

@@

\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-11-1} \end{center}

@@

\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-12-1} \end{center}

@@

\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-13-1} \end{center}

@@

\begin{center}\includegraphics[width=0.95\linewidth]{paper_files/figure-latex/unnamed-chunk-14-1} \end{center}
